Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-05 ms.tex
moving figures around
nearly complete first pass at correlation slope discussion

In the case of the two-component model, based on a spectrum of \PLANCK~and 
DIRBE correlations slopes, we wish to obtain estimates for six free parameters:
$\beta_1$, $\beta_2$, $q_1/q_2$, $f_1$, $T_2$ and the overall spectrum 
normalization $n$. The constraints we employ are the correlation slopes of each
of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz), 140$\mu$m 
(2141 GHz) and 240$\mu$m (1250 GHz) relative to \PLANCK~857 GHz, i.e. 
$dI_{\nu_i}/dI_{857}$. We will refer to the slope for band $\nu_i$ relative to 
\PLANCK~857 GHz as $s_{i,857}$. The slopes for \PLANCK~100-545 GHz are taken 
to be those derived from the relative zero level fits of $\S$\ref{sec:relzero},
and are illustrated by the dashed red lines in plots of Figure \ref{fig:dip}, 
right column. The 857 GHz slope is by definition unity.

@@

Including 857 GHz, we thus have nine correlation slope constraints for six 
free parameters. Including DIRBE 140$\mu$m and 240$\mu$m is critical in making 
this problem sufficiently constrained, and also in providing information near 
the peak of the dust SED at $\sim$140$\mu$m, which is particularly sensitive to
 the presence of a single versus multiple MBB components. % last sentence mentioning
% that the large number of frequency channels and good coverage of the 
% dust SED peak were what made FIRAS so appropriate for FDS99 analysis ??

@@

% hmm it's really seeming like I need to move the color correction section
% to be before this, because I need the \tilde{I} things in this equation

\begin{equation} \label{equ:chi2corr}
\chi^2 = \sum_{i=0}^{8}\frac{\big[s_{i, 857}-n\frac{\tilde{I}_{\nu_i}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}{\tilde{I}_{857}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}\big]^2}{\sigma_{s}^2}
\end{equation}

Where $\nu_i$$\in$\{100, 143, 217, 353, 545, 857, 1250, 2141, 3000\} GHz. Note 
that this formula encompasses the general two-component case. In the single-MBB
case, we take $f_1$=0 and hence $q_1/q_2$, $\beta_1$ and $T_1$ are immaterial, 
but Equation \ref{equ:chi2corr} still applies.

%All comparisons between %\PLANCK~and the FDS99 predictions were made after 
%smoothing both to $1^{\circ}$, subtracting the SMICA CMB model, and ignoring 
%SMICA inpainted pixels. For 100-857 GHz, the linearity between the FDS and 
%\PLANCK~is excellent.

@@

\section{Fitting Procedure}
\label{sec:fitting}

>>>>

In the case of the two-component model, based on a spectrum of \PLANCK~and 
DIRBE correlations slopes, we wish to obtain estimates for six free parameters:
$\beta_1$, $\beta_2$, $q_1/q_2$, $f_1$, $T_2$ and the overall spectrum 
normalization $n$. The constraints we employ are the correlation slopes of each
of the \PLANCK~HFI bands, as well as DIRBE 100$\mu$m (3000 GHz), 140$\mu$m 
(2141 GHz) and 240$\mu$m (1250 GHz) relative to \PLANCK~857 GHz, i.e. 
$dI_{\nu_i}/dI_{857}$. We will refer to the slope for band $\nu_i$ relative to 
\PLANCK~857 GHz as $s_{i,857}$. The slopes for \PLANCK~100-545 GHz are taken 
to be those derived from the relative zero level fits of $\S$\ref{sec:relzero},
and are illustrated by the dashed red lines in the right-hand column plots of 
Figure \ref{fig:dip}. The 857 GHz slope is by definition unity.

@@

Including 857 GHz, we thus have nine correlation slope constraints for six 
free parameters. Including DIRBE 140$\mu$m and 240$\mu$m is critical in making 
this problem sufficiently overconstrained, and also in providing information 
near the peak of the dust SED at $\sim$140$\mu$m, which is particularly 
sensitive to the presence of a single versus multiple MBB components. 
% last sentence mentioning
% that the large number of frequency channels and good coverage of the 
% dust SED peak were what made FIRAS so appropriate for FDS99 analysis ??

@@

\begin{equation} \label{equ:chi2corr}
\chi^2 = \sum_{i=0}^{8}\frac{\big[s_{i, 857}-n\frac{\tilde{I}_{\nu_i}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}{\tilde{I}_{857}(\beta_1, \beta_2, f_1, q_1/q_2, T_2)}\big]^2}{\sigma_{i}^2}
\end{equation}

Where $\nu_i$$\in$\{100, 143, 217, 353, 545, 857, 1250, 2141, 3000\} GHz. Note 
that this formula encompasses the general two-component case. In the single-MBB
case, we take $f_1$=0 and hence $q_1/q_2$, $\beta_1$ and $T_1$ are immaterial, 
but Equation \ref{equ:chi2corr} still applies. Note also that no `priors' have
been included to preferentially drag our results towards agreement with those 
of FDS99.

The results of our chi-squared minimization are listed in Table 
\ref{tab:global}. First (model 1), we fix $\beta_1$, $\beta_2$ ,$q_1/q_2$ and
$f_1$ to the best-fit values from the FDS99 analysis based on DIRBE+FIRAS. We
then allow $n$ and $T_2$ to vary so as to best match our 
DIRBE+\PLANCK~spectrum. This results in a reduced chi-squared of 
$\chi^2_{\nu}$=3.41. Reassuringly, $n$ is quite close to unity. It should be 
noted though that our best-fit $T_2$ is $\sim$0.5 K lower than that found by 
FDS99 for the same values of $\beta_1$, $\beta_2$ ,$q_1/q_2$ and $f_1$.

Next (model 2), we consider the fully-general two-component model, allowing all
 six model parameters to vary. In this case, the reduced chi-squared of the 
best fit is $\chi^2_{\nu}=$1.33, signifying that our introduction of four 
additional free parameters is justified. The best-fit $\beta_1$ and $\beta_2$ 
are both consistent with the corresponding FDS99 values to within 5\%. 
$q_1/q_2$=8.22 represents a $\sim$40\% lower value than found by FDS99, while
$f_1$=0.0458 represents a $\sim$25\% increase relative to FDS99. Again, our
best-fit high-latitude $T_2$ is $\sim$0.5 K lower than the typical value of 
$\langle T_2 \rangle$=16.2 K from FDS99.

Lastly, we calculate the optimal single-MBB fit to the \PLANCK+DIRBE 
correlation slope spectrum. The best-fit single MBB has $\beta$=1.59, 
$T$=19.63, and $\chi^2_{\nu}$=5.65, indicating a significantly worse fit to the
data than our best-fit two-component model (model 2). Thus, our \PLANCK+DIRBE 
correlation slope analysis has confirmed the basic conclusion of FDS99 and 
others e.g. \cite{reach95}, that the FIR/submm dust SED prefers two MBBs to 
just one, but, for the first time, independent of FIRAS. However, it is also
apparent that the improvement in $\chi^2_{\nu}$ for single-MBB versus double
MBB models found here is substantially less dramatic 
($\Delta\chi^2_{\nu}$=4.32) than that found in FDS99 
($\Delta\chi^2_{\nu}$=29.2). This is likely attributable to the exquisite 
narrow-band frequency coverage of FIRAS, especially near the dust SED peak, 
which makes FIRAS a better suited data set than \PLANCK~for a detailed 
analysis of the globally best-fit dust SED model.

% acknowledge that the preference for two MBBs is relatively weak when swapping
% in Planck for FIRAS, probably due to the

@@

\section{MCMC Fitting Procedure}
\label{sec:fitting}
